Dual host-parasite transcriptomes of apicomplexan Eimeria falciformis and its natural mouse host

### 2016-07-20 figuresANDmanuscript/manuscriptBMCformat/manuscript_rnaseq.tex
First additions to MS.tex and some gitignore

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 	OVERVIEW READS PER SAMPLE, LAYOT AS EXPERIMENTAL OVERVIEW
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental overview}
Replicate average of transcripts as order of magnitude for \textit{E. falciformis}/mouse are indicated in Table.... Columns in table represent mouse strains used in infection experiments. Rows represent timepoints post infection plus oocyst and sporozoite samples. The upper part of the table shows data for first infection, and oocyst and sporozoite data. The lower part shows data for challenge infection. Averages were calculated after sample exclusions (see Methods). For exact values, see Table 1.

@@

\section*{Additional Files}
  \subsection*{Additional file 1 --- Sample additional file title}
    Additional file descriptions text (including details of how to
    view the file, if it is in a non-standard format or the file extension).  This might
    refer to a multi-page table or a figure.

  \subsection*{Additional file 2 --- Sample additional file title}
    Additional file descriptions text.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 	OVERVIEW READS PER SAMPLE, LAYOT AS EXPERIMENTAL OVERVIEW
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental overview}
We performed mRNA sequencing of caecum tissue of mice infected with
the parasite \textit{E. falciformis} at different timepoints and for
infections of different mouse strains.

Replicate average of transcripts as order of magnitude for
\textit{E. falciformis}/mouse are indicated in Table.... Columns in
table represent mouse strains used in infection experiments. Rows
represent timepoints post infection plus oocyst and sporozoite
samples. The upper part of the table shows data for first infection,
and oocyst and sporozoite data. The lower part shows data for
challenge infection. Averages were calculated after sample exclusions
(see Methods). For exact values, see Table 1.

@@

\section*{Additional Files}
  \subsection*{Additional file 1 --- Raw and normalized counts }
  Raw and normalized counts for individual samples in our
  study (two compressed csv files).

  \subsection*{Additional file 2 --- Results of statistical tests (edgeR) }
  Fold-changes, p-values and false discovery rates (adjusted p-values)
  are given for all tested contrasts (one compressed csv file).

  \subsection*{Additional file 3 --- Additional methods and resuts }
  % this would be cool but requires special referencing in the text
  % (hard to keep track and hard to fit in the journals referencing
  % system). But we can try.
  Document containing additonal figures and summary tables (pdf).

\subsection*{Additional file 4 --- Results of enrichment analyses (topGO)}
  Tables listing all tested gene sets and resulting significatn GO
  terms.
